Oral anticoagulants

### 2021-01-10 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
splitting gp_practices to ease computational burden

@@

```{r, health-board-modelling}
# system.time(oac_p_hb_cv_models <-
#   regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))
# 
# oac_p_hb_cv_models %>%
#   write_rds("../data/oac_p_hb_cv_models.rds")

@@

```{r}
# system.time(oac_p_hb_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_hb_pre_cv19))
# 
# oac_p_hb_fcsts %>%
#   write_rds("../data/oac_p_hb_fcsts.rds")

@@

```{r, gp-cluster-modelling}
# system.time(oac_p_gp_cluster_cv_models <-
#   regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))
# 
# oac_p_gp_cluster_cv_models %>%
#   write_rds("../data/oac_p_gp_cluster_cv_models.rds")

@@

```{r}
# plan(multisession)
# system.time(oac_p_gp_cluster_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_cluster_pre_cv19))
# plan(sequential)
# 
# oac_p_gp_cluster_fcsts %>%
#   write_rds("../data/oac_p_gp_cluster_fcsts.rds")

@@

```{r, gp-practice-modelling}
regionalCV <- function(data, cv_dist = 6, init = 36, step = 1){

  data %>%
    mutate(datename = yearmonth(datename)) %>%
    model(trend_model1 = TSLM(log(n) ~ trend()),#time series linear model
          trend_model2 = TSLM(log(n) ~ trend() + season("year")),
          ets1 = ETS(log(n) ~ trend()),
          ets2 = ETS(log(n) ~ trend() + season("A")),
          ets3 = ETS(log(n) ~ trend() + season("M")),
          arima = ARIMA(log(n), stepwise = FALSE, approximation = FALSE),
          neur_net = NNETAR(log(n)),
          #fasster = FASSTER(n ~ season("1 year") + trend(1) + fourier(12)),
          comb1 = combination_model(TSLM(log(n) ~ trend()),
                                    ETS(log(n) ~ trend())),
          comb2 = combination_model(TSLM(log(n) ~ trend() + season("year")),
                                    ETS(log(n) ~ trend() + season("A"))),
          stl_dcmp1 = decomposition_model(STL(log(n) ~ trend(),
                                              iterations = 1000,
                                              robust = TRUE),
                                          SNAIVE(season_adjust)),
          stl_dcmp2 = decomposition_model(STL(log(n) ~ trend() + season(),
                                              iterations = 1000,
                                              robust = TRUE),
                                          SNAIVE(season_adjust)),
          s_naive = SNAIVE(log(n)))# %>%
    #as_tibble() # map_dfr() doesn't work on tsibble objects
  }

  plan(cluster) # Set up parallel processing to decrease computation time
  # Prophet models won't run with plan(multisession) so need to be run
  # sequentially. Is it worth trying to write this in Python and pass it back
  # to R?

incomplete_gp <- oac_p_monthly_quantity_gp_pre_cv19 %>% 
    as_tibble() %>% 
    group_by(regional_unit) %>% 
    count() %>% 
    filter(n < 50) %>% 
    .$regional_unit %>% 
    unique()

system.time(oac_p_gp_cv_models <-
  oac_p_monthly_quantity_gp_pre_cv19 %>%
    filter(!regional_unit %in% incomplete_gp) %>%
              regionalCV())

@@

oac_p_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))

>>>>

# Modifying functions to model log(n) as using proportion data
regionalCV <- function(data, cv_dist = 6, init = 36, step = 1){

    data %>%
      mutate(datename = yearmonth(datename)) %>%
      model(trend_model1 = TSLM(log(n) ~ trend()),#time series linear model
            trend_model2 = TSLM(log(n) ~ trend() + season("year")),
            ets1 = ETS(log(n) ~ trend()),
            ets2 = ETS(log(n) ~ trend() + season("A")),
            ets3 = ETS(log(n) ~ trend() + season("M")),
            arima = ARIMA(log(n), stepwise = FALSE, approximation = FALSE),
            neur_net = NNETAR(log(n)),
            comb1 = combination_model(TSLM(log(n) ~ trend()),
                                      ETS(log(n) ~ trend())),
            comb2 = combination_model(TSLM(log(n) ~ trend() + season("year")),
                                      ETS(log(n) ~ trend() + season("A"))),
            stl_dcmp1 = decomposition_model(STL(log(n) ~ trend(),
                                                iterations = 1000,
                                                robust = TRUE),
                                            SNAIVE(season_adjust)),
            stl_dcmp2 = decomposition_model(STL(log(n) ~ trend() + season(),
                                                iterations = 1000,
                                                robust = TRUE),
                                            SNAIVE(season_adjust)),
            s_naive = SNAIVE(log(n)))
  }

  # plan(cluster) # Set up parallel processing to decrease computation time
  plan(multisession) # Set up parallel processing to decrease computation time
  # Prophet models won't run with plan(multisession) so need to be run
  # sequentially. Is it worth trying to write this in Python and pass it back
  # to R?

@@

```{r, health-board-modelling}
system.time(oac_p_hb_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))

oac_p_hb_cv_models %>%
  write_rds("../data/oac_p_hb_cv_models.rds")

@@

```{r}
system.time(oac_p_hb_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_hb_pre_cv19))

oac_p_hb_fcsts %>%
  write_rds("../data/oac_p_hb_fcsts.rds")

@@

```{r, gp-cluster-modelling}
system.time(oac_p_gp_cluster_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))

oac_p_gp_cluster_cv_models %>%
  write_rds("../data/oac_p_gp_cluster_cv_models.rds")

@@

```{r}
plan(multisession)
system.time(oac_p_gp_cluster_fcsts <- 
              regionalJointFcsts(oac_p_monthly_quantity_cluster_pre_cv19))
plan(sequential)

oac_p_gp_cluster_fcsts %>%
  write_rds("../data/oac_p_gp_cluster_fcsts.rds")

@@

```{r, gp-practice-modelling}
incomplete_gp <- # Need to remove GP Practices with incomplete data
  oac_p_monthly_quantity_gp_pre_cv19 %>% 
    as_tibble() %>% 
    group_by(regional_unit) %>% 
    count() %>% 
    filter(n < 50) %>% 
    .$regional_unit %>% 
    unique()

complete_oac_p_monthly_quantity_gp_pre_cv19 <- 
  oac_p_monthly_quantity_gp_pre_cv19 %>% 
  filter(!regional_unit %in% incomplete_gp)

# Splitting practices into separate analyses to ease computational burden
seg_1 <- 
  complete_oac_p_monthly_quantity_gp_pre_cv19$regional_unit %>% 
           unique() %>% 
           .[1:101] %>% 
  as.character()
seg_2 <- 
  complete_oac_p_monthly_quantity_gp_pre_cv19$regional_unit %>% 
           unique() %>% 
           .[102:202] %>% 
  as.character()
seg_3 <- 
  complete_oac_p_monthly_quantity_gp_pre_cv19$regional_unit %>% 
           unique() %>% 
           .[203:303] %>% 
  as.character()
seg_4 <- 
  complete_oac_p_monthly_quantity_gp_pre_cv19$regional_unit %>% 
           unique() %>% 
           .[304:404] %>% 
  as.character()

complete_oac_p_monthly_quantity_gp_pre_cv19_1 <- 
  complete_oac_p_monthly_quantity_gp_pre_cv19 %>% 
  filter(regional_unit %in% seg_1)
complete_oac_p_monthly_quantity_gp_pre_cv19_2 <- 
  complete_oac_p_monthly_quantity_gp_pre_cv19 %>% 
  filter(regional_unit %in% seg_2)
complete_oac_p_monthly_quantity_gp_pre_cv19_3 <- 
  complete_oac_p_monthly_quantity_gp_pre_cv19 %>% 
  filter(regional_unit %in% seg_3)
complete_oac_p_monthly_quantity_gp_pre_cv19_4 <- 
  complete_oac_p_monthly_quantity_gp_pre_cv19 %>% 
  filter(regional_unit %in% seg_4)

# Running regionalCV() on each of the quarter of the data
system.time(oac_p_gp_cv_models_1 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_1 %>%
              regionalCV())
system.time(oac_p_gp_cv_models_2 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_2 %>%
              regionalCV())
system.time(oac_p_gp_cv_models_3 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_3 %>%
              regionalCV())
system.time(oac_p_gp_cv_models_4 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_4 %>%
              regionalCV())

# Joining the separated results
oac_p_gp_cv_models <- 
  rbind(oac_p_gp_cv_models_1,
        oac_p_gp_cv_models_2,
        oac_p_gp_cv_models_3,
        oac_p_gp_cv_models_4)

@@

oac_p_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))
```
